|

### 2024-02-29 docs/paper.qmd
Switched to retracted data version

sd <- readRDS("../data/generated/survey_response.rds")
mr <- readRDS("../data/generated/merged_response.rds")
vars <- read_csv("../data/external/variables.csv", show_col_types = FALSE)
pop <- read_csv("../data/external/invited_authors.csv", show_col_types = FALSE)
```

>>>>

sd <- readRDS("../data/generated/survey_response.rds")
mr <- readRDS("../data/generated/merged_response.rds")
vars <- read_csv("../data/external/variables.csv", show_col_types = FALSE)
pop <- read_csv("../data/external/invited_authors_retracted.csv", show_col_types = FALSE)
```
